Demo: Counterpoint by Construction

### 2019-06-21 doc/farm/farm-abstract.tex
fixed a typo

The last requirement is that the music must end with a cadence,
which is a final motion from the 2nd or 7th degree to the tonic 
(1st degree). 
We impose this requirement by declaring two cadence constructors 
as the base cases of counterpoint.
Thus, we arrive at the following datatype for well-typed counterpoint\footnote{
For readability, we have ommited explicit conversions 
from \texttt{PitchInterval} (which ensures the interval is not dissonant) 
to the general \texttt{Interval}.}.

>>>>

The last requirement is that the music must end with a cadence,
which is a final motion from the 2nd or 7th degree to the tonic 
(1st degree). 
We impose this requirement by declaring two cadence constructors 
as the base cases of counterpoint.
Thus, we arrive at the following datatype for well-typed counterpoint\footnote{
For readability, we have omitted explicit conversions 
from \texttt{PitchInterval} (which ensures the interval is not dissonant) 
to the general \texttt{Interval}.}.
